Self Regulation Ontology Retest Data Report

### 2017-10-03 code/SRO_Report.Rmd
added modified gitignore for workspaces and changed report with new test data release

### Load time 1 data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables.csv')

test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_noDDM.csv')

test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_EZ.csv')

@@

```{r}
test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')

@@

>>>>

### Load time 1 data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables.csv')

test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables_noDDM.csv')

test_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/meaningful_variables_EZ.csv')

@@

```{r}
test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_07-08-2017/variables_exhaustive.csv')

@@

This should not be necessary once releases are matched but for now extract only retest variables from test data.

```{r}
test_data <- test_data[,c(names(retest_data))]
```
